Prepare Data

### 2021-04-14 src/data-processing/prep_data.Rmd
minor edits getting data from qualtrics

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Independent Variable](#independent-variable)
  - [Control Variables](#control-variables)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
renv::snapshot()
source(here::here("src/lib/functions.R"))
```

## Tidy Data

```{r "get data from Qualtrics"}
pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1)  %>%
  select(matches("PreT\\d"), id = ResponseId) %>%
  select(-matches("PreT[26]_NPS_GROUP")) %>%
  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|") %>%
  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|") %>%
  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
  select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
         order_PreT5, order_PreT7, order_PreT) %>%
  mutate(across(matches("PreT5_\\d+"), 
            ~recode(., `15` = 5, `14` = 4, `13` = 3,
                    `12` = 2, `11` = 1)))

tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                  label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("name-[A-Z]"), compromis, id = ResponseId)

pt <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("PT-[A-Z]\\d"), id = ResponseId) %>%
  select(-matches("PT-[A-Z]\\d_NPS_GROUP")) %>%
  unite(order_PT_D1, matches("PT-D1_DO_\\d+"), sep="|") %>%
  unite(order_PT_D, matches("PostTreatment-Defense_DO_PT-D\\d+"), sep="|") %>%
  unite(order_PT_E1, matches("PT-E1_DO_\\d+"), sep="|") %>%
  unite(order_PT_E, matches("PostTreatment-Education_DO_PT-E\\d+"), sep="|") %>%
  unite(order_PT_I1, matches("PT-I1_DO_\\d+"), sep="|") %>%
  unite(order_PT_I, matches("PostTreatment-Immigration_DO_PT-I\\d+"), sep="|") %>%
  unite(order_PT_C1, matches("PT-C1_DO_\\d+"), sep="|") %>%
  unite(order_PT_C, matches("PostTreatment-Corona_DO_PT-C\\d+"), sep="|") %>%
  select(id, `PT-D1_1`:`PT-D1_6`, `PT-D2`:`PT-I1_6`, `PT-I2`:`PT-E1_6`, 
         `PT-E2`: `PT-C1_6`, `PT-C2`:`PT-C4`, order_PT_D1, order_PT_D,
         order_PT_E1, order_PT_E, order_PT_I1, order_PT_I, 
         order_PT_C1, order_PT_C)

bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(id = ResponseId, matches("F\\d"), etnicity) %>%
  unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
  mutate(F1 = recode(F1, `1` = 0, `2` = 1, `3` = 2, `4` = 999)) %>%
  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)

d <- left_join(bg, pret, by = "id")
d <- left_join(d, tr, by = "id")
d <- left_join(d, pt, by = "id")
rm(bg, pret, tr, pt)
```

@@

>>>>

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Check Missing Values](#check-missing-values)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Independent Variable](#independent-variable)
  - [Control Variables](#control-variables)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
renv::snapshot()
```

## Tidy Data
This code chuck downloads the data from Qualtrics using the API and cleans the raw data.

```{r "get data from Qualtrics", results="hide"}
source(here("src/data-processing/tidy_data.R"))
```

@@

## Check Missing Values

We employ the following criteria:

- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.

```{r "check missings"}
